A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Satisfy

\textit{Satisfy-one} traverses the OBDD depth-first and uses backtracking until
a terminal node of the constant function \textbf{1} is encountered. If such a
node is found, the corresponding Boolean function is satisfiable and true is
returned. Furthermore, an array representing the satisfying variable assignment
is assigned. The time complexity for a reduced graph is linear, i.e.
$O(|V_f|)$~\cite{BRYANT86}.

\textit{Satisfy-all} also traverses the OBDD depth-first. Every time the terminal
node having value \textbf{1} is traversed, it is printed. The recursive procedure
terminates as soon as the terminal node having value \textbf{0} is reached. This
results in a time complexity of $O(|V_f| \cdot |S_f|)$, whereas $S_f$ denotes the
satisfying set~\cite{BRYANT86}. \tbr

>>>>

\textit{Satisfy-one} traverses the OBDD depth-first and uses backtracking until
the terminal node of the constant function \textbf{1} is encountered. If this node
is reached, the corresponding Boolean function is satisfiable and \textbf{True}
is returned. Furthermore, an array representing the satisfying variable assignment
is assigned. The time complexity for a reduced graph is linear, i.e.
$O(|V_f|)$~\cite{BRYANT86}.

\textit{Satisfy-all} also traverses the OBDD depth-first. Each time the terminal
node having value \textbf{1} is traversed, the element corresponding to the current
path is printed. The recursive procedure terminates as soon as the terminal node
having value \textbf{0} is reached. This results in a time complexity of
$O(|V_f| \cdot |S_f|)$, whereas $S_f$ denotes the satisfying set~\cite{BRYANT86}.
